사람과 기계의 일자리 경쟁 요인과 협업 방안

### 2020-03-06 tutorial/paper/paper.Rmd
compile with fred key

```{r fred-data-labor-participation, dev="cairo_pdf", out.width="100%", fig.cap="미국 노동참여율 연도별 추이 (1948 - 2018)", eval=FALSE}
library(fredr)
library(xts)
fredr_set_key(FRED_KEY)

>>>>

```{r fred-data-labor-participation, dev="cairo_pdf", out.width="100%", fig.cap="미국 노동참여율 연도별 추이 (1948 - 2018)", eval=TRUE}
library(fredr)
library(xts)
fredr_set_key(FRED_KEY)
